---
title: "Plate_Counts_2020"
output:
  prettydoc::html_pretty:
    theme: cayman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r, echo=FALSE}
library(tidyverse)
library(dplyr)
library(lubridate)
```


```{r, fig.width = 8, fig.height = 6, echo=FALSE}
plate_counts_df_12_5 <- read_csv("2017_plate_counts_fixed_12_5.csv",
    col_types = cols(Dilution_X = col_number(), 
        Half_Plate_Count_TSA_W_SB = col_number(), 
        Full_Plate = col_number(), Hours = col_number(), 
        Count_X_Dil = col_number(), Total_CFU = col_number()),
    locale = locale())
view(plate_counts_df_12_5)

plate_counts_df_12_5 %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-01-30")) %>% 
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank))) +
    ggtitle("2020 Plate Counts Per Tank")
```

# Data for all tanks
```{r, fig.width = 9, fig.height = 6, echo=FALSE}
plate_counts_df_12_5 %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-01-30")) %>%
  filter(Tank %in% c("A High", "B High", "B6", "C High", "D High", "E High", "HT", "P1 High", "P2 High", "P6 High", "P7 High", "P9 High", "P9", "P10", "P10 High")) %>% 
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank")
```

# Data separated by tank since January 7th, 2020
```{r, fig.width = 8.5, fig.height = 11, echo=FALSE}
plate_counts_df_12_5 %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-01-30")) %>%
  filter(Tank %in% c("A High", "B High", "B6", "C High", "D High", "E High", "HT", "P1 High", "P2 High", "P6 High", "P7 High", "P9 High", "P9", "P10", "P10 High")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  facet_wrap(~Tank, ncol=2) +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))

plate_counts_df_12_5 %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-01-30")) %>%
  filter(Tank %in% c("A High", "B High", "B6", "C High", "D High", "E High", "HT", "P1 High", "P2 High", "P6 High", "P7 High", "P9 High", "P9", "P10", "P10 High", "P10 high")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  facet_wrap(~Tank, ncol=2, scales="free_y") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))
```

# Separate by tank after August 12th, 2020, adjusting to no dilutions
```{r, fig.width = 10, fig.height = 8, echo=FALSE}
plate_counts_df_12_5 %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  facet_wrap(~Tank, ncol=2) +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))
```

## A system August to November 2020 using no dilution method
```{r, fig.width = 4, fig.height = 3, echo=FALSE}
plate_counts_df_12_5 %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  filter(Tank %in% c("A High")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))
```

## B system August to November 2020 using no dilution method
```{r, fig.width = 4, fig.height = 3, echo=FALSE}
plate_counts_df_12_5 %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  filter(Tank %in% c("B High")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))
```

## C system August to November 2020 using no dilution method
```{r, fig.width = 4, fig.height = 3, echo=FALSE}
plate_counts_df_12_5 %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  filter(Tank %in% c("C High")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))
```

## D system August to November 2020 using no dilution method
```{r, fig.width = 4, fig.height = 3, echo=FALSE}
plate_counts_df_12_5 %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  filter(Tank %in% c("D High")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))
```

## E system August to November 2020 using no dilution method
```{r, fig.width = 4, fig.height = 3, echo=FALSE}
plate_counts_df_12_5 %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  filter(Tank %in% c("E High")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))
```

## F system August to November 2020 using no dilution method
```{r, fig.width = 4, fig.height = 3, echo=FALSE}
plate_counts_df_12_5 %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  filter(Tank %in% c("F High")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))
```

## P system August to November 2020 using no dilution method
```{r, fig.width = 7, fig.height = 5, echo=FALSE}
plate_counts_df_12_5 %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  filter(Tank %in% c("P1 High", "P2 High", "P6 High", "P7 High", "P9 High", "P10 High")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))

plate_counts_df_12_5 %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  filter(Tank %in% c("P1 High", "P2 High", "P6 High", "P7 High", "P9 High", "P10 High")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12)) +
  facet_wrap(~Tank, ncol = 2, scales ="free_y")
```

## HT August to November 2020 using no dilution method
```{r, fig.width = 6, fig.height = 4, echo=FALSE}
plate_counts_df_12_5 %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  filter(Tank %in% c("HT", "HTGN Post-UV")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))

plate_counts_df_12_5 %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  filter(Tank %in% c("HT", "HTGN Post-UV")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12)) +
  facet_wrap(~Tank, ncol = 2)
```