---
title: "Plate_Counts_2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r, echo=FALSE}
library(tidyverse)
library(dplyr)
library(lubridate)
```

## Data Formatting
```{r, fig.width = 8, fig.height = 6, echo=FALSE}
plate_counts_df <- read_csv("data/2017_plate_counts.csv")
view(plate_counts_df)

X2017_plate_counts_df <- read_csv("2017_plate_counts.csv", 
    col_types = cols(Dilution_X = col_number(), 
        Half_Plate_Count_TSA_W_SB = col_number(), 
        Full_Plate = col_number(), Hours = col_number(), 
        Count_X_Dil = col_number(), Total_CFU = col_number()), 
    locale = locale())
view(X2017_plate_counts_df)


X2017_plate_counts_df %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-01-07")) %>% 
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank))) +
    ggtitle("2020 Plate Counts Per Tank")
```

# Data for all tanks
```{r, fig.width = 9, fig.height = 6, echo=FALSE}
X2017_plate_counts_df %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-01-07")) %>%
  filter(Tank %in% c("A high", "B high", "B6", "C high", "D high", "E high", "HT", "P1 high", "P2 high", "P6 high", "P7 high", "P9 high", "P9", "P10", "P10 high" )) %>% 
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank")
```

# Data separated by tank since January 7th, 2020
```{r, fig.width = 8.5, fig.height = 11, echo=FALSE}
X2017_plate_counts_df %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-01-07")) %>%
  filter(Tank %in% c("A high", "B high", "B6", "C high", "D high", "E high", "HT", "P1 high", "P2 high", "P6 high", "P7 high", "P9 high", "P9", "P10", "P10 high" )) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  facet_wrap(~Tank, ncol=2) +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))

X2017_plate_counts_df %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-01-07")) %>%
  filter(Tank %in% c("A high", "B high", "B6", "C high", "D high", "E high", "HT", "P1 high", "P2 high", "P6 high", "P7 high", "P9 high", "P9", "P10", "P10 high" )) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  facet_wrap(~Tank, ncol=2, scales="free_y") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))
```

# Separate by tank after August 12th, 2020, adjusting to no dilutions
```{r, fig.width = 10, fig.height = 8, echo=FALSE}
X2017_plate_counts_df %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  facet_wrap(~Tank, ncol=2) +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))
```

## A system 2020 using no dilution method
```{r, fig.width = 4, fig.height = 3, echo=FALSE}
X2017_plate_counts_df %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  filter(Tank %in% c("A high")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))
```

## B system 2020 using no dilution method
```{r, fig.width = 4, fig.height = 3, echo=FALSE}
X2017_plate_counts_df %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  filter(Tank %in% c("B high")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))
```

## C system 2020 using no dilution method
```{r, fig.width = 4, fig.height = 3, echo=FALSE}
X2017_plate_counts_df %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  filter(Tank %in% c("C high")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))
```

## D system 2020 using no dilution method
```{r, fig.width = 4, fig.height = 3, echo=FALSE}
X2017_plate_counts_df %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  filter(Tank %in% c("D high")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))
```

## E system 2020 using no dilution method
```{r, fig.width = 4, fig.height = 3, echo=FALSE}
X2017_plate_counts_df %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  filter(Tank %in% c("E high")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))
```

## F system 2020 using no dilution method
```{r, fig.width = 4, fig.height = 3, echo=FALSE}
X2017_plate_counts_df %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  filter(Tank %in% c("F high")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))
```

## P system 2020 using no dilution method
```{r, fig.width = 7, fig.height = 5, echo=FALSE}
X2017_plate_counts_df %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  filter(Tank %in% c("P1 high", "P2 high", "P6 high", "P7 high", "P9 high", "P10 high")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))

X2017_plate_counts_df %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  filter(Tank %in% c("P1 high", "P2 high", "P6 high", "P7 high", "P9 high", "P10 high")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12)) +
  facet_wrap(~Tank, ncol=2, scales="free_y")
```

## HT 2020 using no dilution method
```{r, fig.width = 6, fig.height = 4, echo=FALSE}
X2017_plate_counts_df %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  filter(Tank %in% c("HT", "HT GN Post-UV")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12))

X2017_plate_counts_df %>% 
  group_by(Date_Read, Tank, Total_CFU) %>% 
  filter(Date_Read >= as.Date("2020-08-12")) %>%
  filter(Tank %in% c("HT", "HT GN Post-UV")) %>%
  ggplot(aes(x = Date_Read, y = Total_CFU)) +
  geom_point((aes(color = Tank))) +
    geom_line((aes(color = Tank, group = Tank))) +
    ggtitle("2020_Plate_Counts_Per_Tank") +
  labs(x = "Date", y = "Total_Colony_Forming_Units") +
  theme_light() +
  theme(text = element_text (size = 12)) +
  facet_wrap(~Tank, ncol=2)
```